---
title: "Midwest Load Model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r error=TRUE}

##load important packages
require(deSolve)
library(lme4)
library(plotrix)
library(ggplot2)
library(reshape2)
library(reshape)
library(brglm)
library(MASS)
library(boot)
library(bbmle)
library(gridExtra)
library(knitr)
```

```{r error=TRUE}

##params##
#example - read in data to determine mean, sd
bins=200
x_s=seq(0,5,length=bins) #x value of rectangle
h_x=dnorm(x_s,mean=2.5,sd=1) #height of rectangle#integral of the distance b/t xi and next xi2 for a gamma dist w/ whatever shape and rate params i choose
plot(x_s,h_x)
h_x=h_x[is.finite(h_x)] 
sum(h_x)

ic2=NA;ic=NA
bins=200
num.step=NA
num.step=seq(0,5, length=bins)


#integrate each rectangle to get the frac of population in each bin
for (i in 1:length(num.step)){
  ic=integrate(dnorm,num.step[i],num.step[i+1],mean=2.5,sd=1)$value
  ic2=c(ic2,ic)
}
#will produce error message because of last block, but works

#```
num.step[is.na(ic2)]=NA
ic2 <- ic2[!is.na(ic2)]
num.step <- num.step[!is.na(num.step)]


sum(ic2,na.rm=T);length(ic2)

#length of q_x will be the same as x_mids, and sum of q_x*x equal 1
#s_start will equal q_x
min_size=min(num.step)
max_size=max(num.step)
# Set the edges of the discretized kernel (the edges of the rectangles in the distribution)
bins=bins-1
bnd = min_size+c(0:bins)*(max_size-min_size) / bins

# Set the midpoints of the discretizing kernel. Using midpoint rule for evaluation
#these are the midpoints - the y's you will use for susceptibility
y_e = 0.5 * (bnd[1:bins] + bnd[2:(bins + 1)])
y_b = 0.5 * (bnd[1:bins] + bnd[2:(bins + 1)])


# Width of cells
h_e = y_e[2] - y_e[1]
h_b = y_b[2] - y_b[1]

init_loads=ic2

sum(init_loads)

plot(y_e,init_loads)
plot(y_b,init_loads*100)

```

Now code the model and ODES:
```{r cars}

##heterogeneous model in continuous times
si.het.model <- function (t, x, params) {
  S_t <- x[1]
  I_t <- x[2:200]#:3002
  E_t<- x[201]
  C_t<- x[202:400]
  ## now extract the parameters
  beta_sc <- params["beta_sc"]
  beta_si <- params["beta_si"]
  #right now, growth isn't incorporated, all reflected in starting load..
  #growth <- params["growth"]
  alpha <- params["alpha"]
  imm_s <- params["imm"]
  imm_i <- params["imm2"]#immigration of infected bat
  c_scalar <-params["c_scalar"]
  ## now code the model equations
  ##need to fix C_t - needs to be proportion
  dS.dt <- -(
    sum(y_b*beta_si*sum(I_t)*S_t)+
    sum(y_e*c_scalar*beta_sc*S_t*((sum(C_t)/(sum(C_t)+E_t))))
    )+
    (imm_s*(S_t+sum(I_t)))
  
  dI.dt <- (
    (y_b*beta_si*(I_t)*S_t)+#bat to bat - based on load
    (y_e*beta_sc*c_scalar*S_t*(sum(C_t)/(sum(C_t)+E_t)))+#bat to environment - based on load
      (imm_i*(S_t+sum(I_t)))-
      (alpha*I_t*y_b)#immigration of infecteds
  )  
  #environment
  dE.dt <- -sum(beta_sc*y_b*(I_t)*(1-(sum(C_t)/(sum(C_t)+E_t))))
  dC.dt <- beta_sc*y_b*(I_t)*(1-(sum(C_t)/(sum(C_t)+E_t)))
  
  #dI.dt <- sum(y*beta*I_t*V_t)-gamma*I_t-alpha*I_t#+(y*beta*sum(I_t)*S_t))
  
  dxdt <- c(dS.dt,dI.dt,dE.dt,dC.dt)#,dN.dt#dS.dt,
  ## return result as a list!
  list(dxdt)
}
```

Now, run the model.

```{r init}
##. DESCRIBE STARTING CONDITIONS AND RUN MODEL
#Need to run these starting conditions if using analytical solution
N_I=50
S_0=50
I_0=init_loads*N_I #number of individuals in each susceptibility class
sum(I_0, na.rm=T)
N_I=50
E_0=50
C_0=init_loads*N_I #number of contaminated areas
sum(C_0, na.rm=T)



times<- seq(from=1, to=50, by=.1)
xstart <-c(S_t=S_0,I_t=I_0,E_t=E_0,C_t=C_0)#S_t=S_0,
#s will equal q_x,
#initial params
params <- c( beta_sc=.00001,
             beta_si=.00001,
             alpha=.00001,
             imm_i=.00001,
             imm_s=.00001,
             c_scalar=.00001)

c_scalar=.00001;imm_s=.00001;imm_i=.00001;alpha=.00001;beta_si=.00001;beta_sc=.00001

out <- ode(
  func=si.het.model,
  y=xstart,
  times=times,
  parms=params
)
```
The ODE solver ran, and no error messages

```{r model out}

out=as.data.frame(out)
outplot=melt(out,id.var="time")
head(outplot)

```
The output makes no sense, and the values never ran past initialization.